\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-21 chapters/3_algorithm.tex
Update figs and minor changes

In Algorithm \ref{main_alg}, we provide a simplified pseudo-code for the proposed \algname{} algorithm that is based on a bottom-up approach starting with each node assigned to its own cluster and iteratively merges pairs of adjacent clusters. It starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}). After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.

A second variant of Algorithm \ref{main_alg}, with option \texttt{addCannotLinkConstraints=True}, introduces \emph{cannot-link constraints}, which represent mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering. This variant 
selects the pair of clusters with the highest absolute interaction $|\interact(S_u, S_v)|$, so that the most attractive and the most repulsive pairs are analyzed first (see example in Fig. \ref{subfig:with_constraints}). If the interaction is repulsive, then the two clusters are constrained. If it is attractive, then they are merged, provided that they were not already previously constrained. 
The algorithm stops when all the remaining clusters are constrained.
% The algorithm that we will present in the next section iteratively performs a sequence of so-called \emph{edge contractions} on the original graph $\mathcal{G}(V,E,w^+, w^-)$.
% The graph clustering algorithm we will present in Sec. \ref{sec:algorithm} is a bottom-up approach starting with each node assigned to its own cluster and iteratively merging clusters. During the agglomeration, the current clustering $\Pi$ is represented by a \emph{contracted graph} $\mathcal{G'}(\mathcal{G}, \Pi)$, such that each of its nodes represents a cluster $S \in \Pi$ and \emph{adjacent} clusters are linked by an edge. 
% For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$. Thus, we can easily recompute these interactions by using a simple \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$. As an example, given the single-linkage criterion defined in Eq. \ref{eq:max_linkage}, the interaction between $S_u \cup S_v$ and one of its neighbors $S_t$ is simply given by:
% \begin{equation}
%   \interact_{S_u \cup S_v,S_t} = f( \interact_{S_u,S_t}, \interact_{S_v,S_t}) = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) = \max \{ \tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}) \}
% \end{equation}
% All the update rules tested in this article are listed in Table \ref{tab:linkage-criteria}.

@@

In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
 the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see \UPDATE{left panel} of Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} and Table \ref{tab:linkage-criteria}, unsigned graphs).

>>>>

In Algorithm \ref{main_alg}, we provide a simplified pseudo-code for the proposed \algname{} algorithm that is based on a bottom-up approach starting with each node assigned to its own cluster and iteratively merging pairs of adjacent clusters. The algorithm has two variants, depending on the boolean value of the input option \texttt{addCannotLinkConstraints}. The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}). After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.

In the second variant, when \texttt{addCannotLinkConstraints=True}, Algorithm \ref{main_alg} also introduces \emph{cannot-link constraints}, which represent mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering. This variant 
selects the pair of clusters with the highest absolute interaction $|\interact(S_u, S_v)|$, so that the most attractive and the most repulsive pairs are analyzed first (see example in Fig. \ref{subfig:with_constraints}). If the interaction is repulsive, then the two clusters are constrained. If it is attractive, then they are merged, provided that they were not already previously constrained. 
The algorithm stops when all the remaining clusters are constrained.
% The algorithm that we will present in the next section iteratively performs a sequence of so-called \emph{edge contractions} on the original graph $\mathcal{G}(V,E,w^+, w^-)$.
% The graph clustering algorithm we will present in Sec. \ref{sec:algorithm} is a bottom-up approach starting with each node assigned to its own cluster and iteratively merging clusters. During the agglomeration, the current clustering $\Pi$ is represented by a \emph{contracted graph} $\mathcal{G'}(\mathcal{G}, \Pi)$, such that each of its nodes represents a cluster $S \in \Pi$ and \emph{adjacent} clusters are linked by an edge. 
% For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$. Thus, we can easily recompute these interactions by using a simple \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$. As an example, given the single-linkage criterion defined in Eq. \ref{eq:max_linkage}, the interaction between $S_u \cup S_v$ and one of its neighbors $S_t$ is simply given by:
% \begin{equation}
%   \interact_{S_u \cup S_v,S_t} = f( \interact_{S_u,S_t}, \interact_{S_v,S_t}) = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) = \max \{ \tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}) \}
% \end{equation}
% All the update rules tested in this article are listed in Table \ref{tab:linkage-criteria}.

@@

In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
 the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see bottom panel of Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} and Table \ref{tab:linkage-criteria}, unsigned graphs).

### 2019-05-21 chapters/5_experiments_cityscapes.tex
Update figs; add extended CS results
Update figs and minor changes

Results are summarized in Table \ref{tab:results_cityscapes_val} and confirm our findings on neuron-segmentation: \algname{} with average linkage achieves the best scores, whereas other linkage tend to introduce more false region-splits, like \emph{Abs. Max.}, or false region-merge, like \emph{Sum}. In Appendix, \TODO{Table \ref{tab:extended_results_cityscapes}} includes all other tested linkage. MultiStepHAC requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.

\begin{figure}[t]
\centering
\begin{minipage}[T]{0.59\textwidth}
    \centering
    \footnotesize
        \begin{tabular}{l|l|cc}
           & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
          Pipeline & method & \textsc{No} & \textsc{Yes} \\ \midrule
DWT \cite{bai2017deep} & - & 21.2 & - \\
SGN \cite{liu2017sgn} & - & 29.2 & - \\
Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
 & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
\multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & \UPDATE{33.0} & -  \\
 % & \algname{} Max &   24.3  &   32.5  \\
 & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
 & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
 % & \algname{} Min &  0    & 0  \\
        \end{tabular}
    \captionof{table}{Average Precision (AP) scores on the cityscapes validation set achieved by the tested pipelines}
    \label{tab:results_cityscapes_val}
\end{minipage}\hfill
\begin{minipage}[T]{0.37\textwidth}
    \centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_2.pdf} % left bottom right top
\end{minipage}
\end{figure}

>>>>

Results are summarized in Table \ref{tab:results_cityscapes_val} and confirm our findings on neuron-segmentation: \algname{} with average linkage achieves the best scores, whereas other linkage tend to introduce more false region-splits, like \emph{Abs. Max.}, or false region-merge, like \emph{Sum}. In Appendix, Table \ref{tab:extended_results_cityscapes_val} includes all other tested linkage. MultiStepHAC requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.

\begin{figure}[t]
\centering
\begin{minipage}[T]{0.59\textwidth}
    \centering
    \footnotesize
        \begin{tabular}{l|l|cc}
           & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
          Pipeline & method & \textsc{No} & \textsc{Yes} \\ \midrule
DWT \cite{bai2017deep} & - & 21.2 & - \\
SGN \cite{liu2017sgn} & - & 29.2 & - \\
Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
 & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
\multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 & -  \\
 % & \algname{} Max &   24.3  &   32.5  \\
 & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
 & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
 % & \algname{} Min &  0    & 0  \\
        \end{tabular}
    \captionof{table}{Average Precision (AP) scores on the cityscapes validation set achieved by the tested pipelines}
    \label{tab:results_cityscapes_val}
\end{minipage}\hfill
\begin{minipage}[T]{0.37\textwidth}
    \centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_2.pdf} % left bottom right top
\end{minipage}
\end{figure}

### 2019-05-21 chapters/5_experiments_compare_rules.tex
Update figs and minor changes

\textbf{Additional methods tested } We compare the performances of \algname{} with other basic and state-of-the-art post-processing methods. To ensure a fair comparison, we test all methods on the same predictions of our CNN model. As basic method, we perform a simple thresholding (THRESH) by running connected components on a boundary map generated from the CNN affinities (see Appendix \ref{sec:cremi_details} for more details on this and the following methods). On the other hand, most of state-of-the-art methods for neuron-segmentation first generates 2D superpixels and then apply a graph partitioning algorithm, since this approach so far proved to be the most reliable that could scale up to the size of the problem. Superpixels are usually computed with a watershed algorithm seeded at the maxima of a boundary distance transform (WSDT). The algorithms employed in our comparison to partition the superpixel graph were given by \algname{} (WSDT+\algname{}) or approximations of the multicut (WSDT+MC) and lifted multicut (WSDT+LMC) problems.

>>>>

\textbf{Additional methods tested } We compare the performances of \algname{} with other basic and state-of-the-art post-processing methods. To ensure a fair comparison, we test all methods on the same predictions of our CNN model. As basic method, we perform a simple thresholding (THRESH) by running connected components on a boundary map generated from the CNN affinities (see Appendix \ref{sec:cremi_details} for more details on this and the following methods). On the other hand, most of state-of-the-art methods for neuron-segmentation first generates 2D superpixels and then apply a graph partitioning algorithm, since this approach so far proved to be the most reliable that could scale up to the size of the problem. Superpixels are usually computed with a watershed algorithm seeded at the maxima of a boundary distance transform (WSDT). The algorithms employed in our comparison to partition the superpixel graph were given by approximations of the multicut (WSDT+MC) and lifted multicut (WSDT+LMC) problems.

### 2019-05-21 chapters/5_experiments_noise.tex
Update figs and minor changes

\subsection{Results and discussion}\label{sec:results}
% \subsection{In-depth comparison of different linkage criteria for \algname{}} 
\textbf{Comparison results } Table \ref{tab:results_cremi_train} shows how \algname{} compares to other tested post-processing methods applied to the predictions of our model. 
% The poor scores achieved by THRESH highlight the difficulty of the task. 
\algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage). The remarkably competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem. 
In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with Average linkage even achieved significantly superior scores compared to other methods based on WSDT superpixels.
Thus, this method offers a simple and successful approach that grow the clusters starting directly from pixels and had the advantage of avoiding potential errors in the superpixel generation. In fact, generating for example good quality WSDT superpixels requires to tune several parameters.   
%Our hypothesis to explain this superior performances is that, currently, there are not good ways of generating superpixels that can take the long-range predictions of the CNN into account. 
%It is of course possible to make use of long-range predictions to compute the edge weights of the superpixel graph, but, in our experience, this process usually involves a lot of parameter tuning and trial and error. 
In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets and present an extended version of Table \ref{tab:results_cremi_train} including all tested \algname{} algorithms.
Fig. \ref{fig:cremi_comparison} highlights some failure cases of the different agglomerative algorithms included in our framework.

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}[t]{l|l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \makecell[l]{\algname{}\\ Linkage} & \makecell{Cremi-Score \\(lower is better)} \\ \midrule 
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{\algname{}} & \textbf{Average}& \textbf{0.226}  \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.282 \\
DTWS + MC & -& 0.310 \\
DTWS + LMC & -& 0.317 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.322 \\
GAEC \cite{keuper2015efficient} & Sum & 0.334 \\
THRESH &-& 1.521 \\ 
% \textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
% Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
% DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
% DTWS + MC & -& 0.903 $\pm$ 0.017 \\
% % DTWS + avgHC &-& \\
% % DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% % DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
% Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
% GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
% THRESH &-& 0.221  $\pm$ 0.067 \\ 
% % DTWS + \algname{} & Average& \TODO{} \\
% % DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{Cremi-Scores achieved by different post-processing methods. Scores are averaged over the three CREMI training samples}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{Cremi-Score \\(lower is better)}  \\ \midrule
Our UNet + DTWS + LMC &  \textbf{0.221}\\
PNI-UNet & 0.228 \\
Our UNet + \algname{} Avg-Linkage & 0.241 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 \\
CRUNet \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
% Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
% PNI-UNet & 0.228 & 0.116 \\
% Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
% MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
% CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
% LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
        \vspace*{1.1em}
    \captionof{table}{Current leaderboard of the CREMI challenge with the Cremi-Scores averaged over the three test samples}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    %     \begin{subfigure}[t]{0.49 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}

@@

        \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.2in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
        \caption{Without long-range edges} \label{fig:merge_noise_only_direct}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.20in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
        \caption{With 10\% long-range edges} \label{fig:merge_noise_with_long_range}
    \end{subfigure}
\caption{\algname{} sensitivity to noise: performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions. In all experiments the average linkage proved to be the most robust. Solid lines represent median values over 30 experiments. Values between the 25th and the 75th percentile are shown in shade areas. The two set of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). On the right, 10\% of the long-range CNN predictions were randomly added to the grid-graph. 
%\textbf{Bottom}: Multicut objective (Eq. \ref{eq:multicut_obj}), measuring how balanced the final clusterings are (lower is better); for a clearer comparison, an offset is added to the energy values, so that the method achieving the lowest energy is always assigned to value zero. 
}\label{fig:noise_plots}
\end{figure}
% \begin{minipage}[b]{0.48\textwidth}
% % \begin{figure}
%         % \begin{subfigure}[t]{0.48 \textwidth}
%         \centering
%         \includegraphics[width=0.98\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}
%         \captionof{subfigure}{Merge-biased opensimplex noise} \label{fig:thresh}
%     \end{minipage}\hfil
% \begin{minipage}[b]{0.48\textwidth}
%     % \end{subfigure}%
%     % \begin{subfigure}[t]{0.48 \textwidth}
%         \centering
%         \includegraphics[width=0.98\textwidth,trim=0.29in 0.31in 0.31in 0.31in,clip]{./figs/split_noise.pdf}
%         \captionof{subfigure}{Split-biased opensimplex noise} \label{fig:ws}
%     % \end{subfigure}
% \captionof{figure}{Plot illustrating Adapted RAND scores achieved by UGACA and different update rules when noise is added to the edge weights... Solid lines represent median values, whereas values between the 25th and the 75th percentile are shown in shade areas.    \TODO{Label which uses only local-neighbors and which uses long-range connections}}\label{fig:noise_plots}
% % \end{figure}

@@

\textbf{Sum linkage } 
% The \emph{Sum} linkage generally outputs the most balanced graph partitioning according to the objective defined in Eq. \ref{eq:multicut_obj} and is then confirmed to be a good choice for initializing more complex approximations of the multicut optimization problem like \cite{beier2016efficient}. 
All our experiments show that \algname{} with \emph{Sum} linkage is the algorithm with the highest tendency to under-cluster and incorrectly merge segments (see Fig. \ref{fig:cremi_comparison} for an example). This property is related to the empirical observation that a \emph{Sum} statistic tends to grow clusters one after the other, as shown in Fig. \ref{fig:intro_figure} by the quite unique agglomeration order of the \emph{Sum} statistic. An intuitive explanation of this fact is the following: initially, most of the infra-cluster nodes present similar attractive interactions between each others; when the two nodes sharing the most attractive interaction are merged, there is a high chance that they both share an attractive interaction with a common neighboring node, so the new interaction with this common neighbor will be immediately assigned to a high priority in the agglomeration, given by the sum of two high weights; this usually starts a ``chain reaction'', where only a single cluster is agglomerated at the beginning. On the other hand, as we also see in Fig. \ref{fig:intro_figure}, other linkage criteria like \emph{Average} or \emph{Abs Max} grow clusters of similar sizes in parallel and accumulate in this way much more reliable inter-cluster statistics.

>>>>

\subsection{Results and discussion}\label{sec:results}
% \subsection{In-depth comparison of different linkage criteria for \algname{}} 
\textbf{Comparison results } Table \ref{tab:results_cremi_train} shows how \algname{} compares to other tested post-processing methods applied to the predictions of our model. 
% The poor scores achieved by THRESH highlight the difficulty of the task. 
\algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage). The remarkably competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem. 
In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with \emph{Average} linkage even achieved significantly superior scores compared to other methods based on WSDT superpixels.
This shows that this method offers a simple and successful approach growing clusters starting directly from pixels and had the advantage of avoiding potential errors in the superpixel generation. In fact, generating for example good quality WSDT superpixels requires to tune several parameters.   
%Our hypothesis to explain this superior performances is that, currently, there are not good ways of generating superpixels that can take the long-range predictions of the CNN into account. 
%It is of course possible to make use of long-range predictions to compute the edge weights of the superpixel graph, but, in our experience, this process usually involves a lot of parameter tuning and trial and error. 
Moreover, superpixel generation does not usually make use of the long-range predictions of the CNN and, in our experiments, using them to compute the weights of the edges in the superpixel graph did not change the final scores.
In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets and present an extended version of Table \ref{tab:results_cremi_train} including all tested \algname{} linkage.
Fig. \ref{fig:cremi_comparison} highlights some failure cases of the different agglomerative algorithms included in our framework.

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}[t]{l|l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \makecell[l]{\algname{}\\ Linkage} & \makecell{Cremi-Score \\(lower is better)} \\ \midrule 
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{\algname{}} & \textbf{Average}& \textbf{0.226}  \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.282 \\
DTWS + MC & -& 0.310 \\
DTWS + LMC & -& 0.317 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.322 \\
GAEC \cite{keuper2015efficient} & Sum & 0.334 \\
THRESH &-& 1.521 \\ 
% \textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
% Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
% DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
% DTWS + MC & -& 0.903 $\pm$ 0.017 \\
% % DTWS + avgHC &-& \\
% % DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% % DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
% Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
% GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
% THRESH &-& 0.221  $\pm$ 0.067 \\ 
% % DTWS + \algname{} & Average& \TODO{} \\
% % DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{Cremi-Scores achieved by different post-processing methods. Scores are averaged over the three CREMI training samples}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{Cremi-Score \\(lower is better)}  \\ \midrule
\textbf{Our UNet + DTWS + LMC} &  \textbf{0.221}\\
PNI-UNet \UPDATE{[REF?]} & 0.228 \\
Our UNet + \algname{} Avg-Linkage & 0.241 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 \\
CRUNet \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
% Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
% PNI-UNet & 0.228 & 0.116 \\
% Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
% MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
% CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
% LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
        \vspace*{1.1em}
    \captionof{table}{Current leaderboard of the CREMI challenge with the Cremi-Scores averaged over the three test samples}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    %     \begin{subfigure}[t]{0.49 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}

@@

        \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.2in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
        \caption{No long-range predictions: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.20in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
        \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
    \end{subfigure}
\caption{\algname{} sensitivity to noise:  average linkage proved to be the most robust. Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions.  Solid lines represent median values over 30 experiments. Values between the 25th and the 75th percentile are shown in shade areas. The two set of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). For each experiment, some of the long-range CNN predictions were randomly selected and added them to pixel grid-graph with probability $p_{\mathrm{long}}$.
%\textbf{Bottom}: Multicut objective (Eq. \ref{eq:multicut_obj}), measuring how balanced the final clusterings are (lower is better); for a clearer comparison, an offset is added to the energy values, so that the method achieving the lowest energy is always assigned to value zero. 
}\label{fig:noise_plots}
\end{figure}
% \begin{minipage}[b]{0.48\textwidth}
% % \begin{figure}
%         % \begin{subfigure}[t]{0.48 \textwidth}
%         \centering
%         \includegraphics[width=0.98\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}
%         \captionof{subfigure}{Merge-biased opensimplex noise} \label{fig:thresh}
%     \end{minipage}\hfil
% \begin{minipage}[b]{0.48\textwidth}
%     % \end{subfigure}%
%     % \begin{subfigure}[t]{0.48 \textwidth}
%         \centering
%         \includegraphics[width=0.98\textwidth,trim=0.29in 0.31in 0.31in 0.31in,clip]{./figs/split_noise.pdf}
%         \captionof{subfigure}{Split-biased opensimplex noise} \label{fig:ws}
%     % \end{subfigure}
% \captionof{figure}{Plot illustrating Adapted RAND scores achieved by UGACA and different update rules when noise is added to the edge weights... Solid lines represent median values, whereas values between the 25th and the 75th percentile are shown in shade areas.    \TODO{Label which uses only local-neighbors and which uses long-range connections}}\label{fig:noise_plots}
% % \end{figure}

@@

\textbf{Sum linkage } 
% The \emph{Sum} linkage generally outputs the most balanced graph partitioning according to the objective defined in Eq. \ref{eq:multicut_obj} and is then confirmed to be a good choice for initializing more complex approximations of the multicut optimization problem like \cite{beier2016efficient}. 
All our experiments show that \algname{} with \emph{Sum} linkage is the algorithm with the highest tendency to under-cluster and incorrectly merge segments (see Fig. \ref{fig:cremi_comparison} for an example). This property is related to the empirical observation that a \emph{Sum} statistic tends to grow clusters one after the other, as shown in Fig. \ref{fig:intro_figure} by the quite unique agglomeration order of the \emph{Sum} statistic. An intuitive explanation of this fact is the following: initially, most of the intra-cluster nodes present similar attractive interactions between each others; when the two nodes sharing the most attractive interaction are merged, there is a high chance that they both share an attractive interaction with a common neighboring node, so the new interaction with this common neighbor will be immediately assigned to a high priority in the agglomeration, given by the sum of two high weights; this usually starts a ``chain reaction'', where only a single cluster is agglomerated at the beginning. On the other hand, as we also see in Fig. \ref{fig:intro_figure}, other linkage criteria like \emph{Average} or \emph{Abs Max} grow clusters of similar sizes in parallel and accumulate in this way much more reliable inter-cluster statistics.

### 2019-05-21 chapters/6_conclusions.tex
Update figs and minor changes

% !TEX root = ../agglo_clust_review.tex
\section{Conclusion}
We have presented a novel theoretical framework for agglomerative clustering of graphs with both positive and negative weights and we have shown that several existing clustering algorithms, like the Mutex Watershed, can be reformulated as special cases of one underlying agglomerative algorithm. This framework also allowed us to introduce new algorithms, one of which (based on an average linkage) outperformed all the others and proved to be a simple and remarkably robust approach to process short- and long-range predictions of a CNN applied to an instance segmentation task.
On biological images, this simple average agglomeration algorithm can represent a valuable choice for an user that is not willing to spend a lot of time tuning complex task-dependent pipelines. % or test several dataset-dependent

>>>>

% !TEX root = ../agglo_clust_review.tex
\section{Conclusion}
We have presented a novel theoretical framework for agglomerative clustering of graphs with both positive and negative weights and we have shown that several existing clustering algorithms, e.g. the Mutex Watershed \cite{wolf2018mutex}, can be reformulated as special cases of one underlying agglomerative algorithm. This framework also allowed us to introduce new algorithms, one of which, based on an average linkage, outperformed all the others and proved to be a simple and remarkably robust approach to process short- and long-range predictions of a CNN applied to an instance segmentation task.
On biological images, this simple average agglomeration algorithm can represent a valuable choice for an user that is not willing to spend much time tuning complex task-dependent pipelines based on superpixels. % or test several dataset-dependent
